---
title: "Eye Tracking Calibration Experiment"
output: html_notebook
---

Loading necessary packages into the environment.

```{r message=FALSE, warning=FALSE}
library(jsonlite)
library(dplyr)
library(stringr)
library(tidyr)
```

Turn off dplyr summarize warnings

```{r}
options(dplyr.summarise.inform=F)
```

Read in the data and organize into a tibble.

```{r}
data.files <- list.files('data', full.names = T)
json.data <- lapply(data.files, function(file){
  data <- fromJSON(file)
  subject_id <- str_split(file, "-|\\.")[[1]][2]
  data <- data %>% mutate(subject_id = subject_id)
  return(data)
})
raw.data <- bind_rows(json.data)
```

Filter out anyone who declined to include their data in the research data set.

```{r}
declined.subjects <- (raw.data %>% filter(question == "consent" & response == 1))$subject_id
all.data <- raw.data %>% filter(!subject_id %in% declined.subjects)
```

Convert columns to correct types

```{r}

```


Summarize the sampling rate (gaze points estimated per second) for each participant

```{r}
sampling.rate.data <- all.data %>% 
  filter(trial_type == "webgazer-validate") %>%
  group_by(subject_id) %>%
  summarize(sampling_rate_mean = mean(samples_per_sec), sampling_rate_sd = sd(samples_per_sec))
```

Create a long-form data frame of validation data per point
```{r}
validation.data <- all.data %>%
  filter(trial_type == "webgazer-validate") %>% 
  unnest(cols=c(raw_gaze, percent_in_roi, average_offset, validation_points))
```

Label each point type
```{r}
validation.data <- validation.data %>%
  